### 2015-08-21 LaTeX/RhodiumTheory.tex
recompiled with new intro
syria example?

% Note to Ben: Should we have a capital city and any city hypothesis?

@@

@@

% Note to Ben: If you have more to add about Mexico here that might be good

>>>>

@@

More recently, economic productivity in Syria has ground to a halt due to its ongoing civil war. Fighting in Syria has been widespread with particularly bloody battles of attrition fought over some of the country's largest cities. Both Aleppo and Damascus have been divided neighborhood-by-neighborhood by the Assad regime and various armed groups vying for control of the cities. Simultaneously, Syria's economy has shrunk dramatically.

@@
